---
title: "BTS_scraping"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tuber) 
library(magrittr) 
library(tidyverse)
library(purrr) 
library(tm)
library(ggplot2)
library(tidytext)
library(stringr)
library(textdata)
library(lubridate)
library(knitr)
library(stargazer)
library(cluster)
library(tau)
library(stm)
library(quanteda)
library(furrr)

set.seed(12345)
```

##Google Authentification
#Note: to skip scraping and load full scraped dataset, see below

```{r}

client_id <- "" #insert client id here
client_secret <- "" #insert here

# use the youtube oauth 
yt_oauth(app_id = client_id,
         app_secret = client_secret,
         token = "")
```

##IDs

```{r}
#Six main videos
vids <- c("9SmQOZWNyWE", "jzptPcPLCnA", "wAXcMD5dOBA", "NWwPyY7OHig", "wT6qgOBRrps", "N11sD4isDRI")

#vid_ids <- as.vector(vids$contentDetails.videoId)
```


##Vid Stats

```{r}

#getting video details for all vids (title, tags, etc)
dat_details <- map_dfr(vids, get_video_details) %>%
  unnest()

details <- dat_details %>%
  filter(grepl("title", items)) %>%
  unnest() #removing unnecessary data

#video titles
title <- c("BTS - 'Permission to Dance' performed at the United Nations General Assembly | SDGs | Official Video", "President Moon Jae-in & BTS at the Sustainable Development Goals Moment | United Nations (English)", "BTS Shine Spotlight on the United Nations as Envoys of the President of the Republic of Korea", "BTS partners with Korean president as special presidential envoys | Nightline", "🇰🇷 Republic of Korea - President Addresses General Debate, 76th Session (English) | #UNGA", "[LIVE] SDG Moment 2021 (#BTS)")


#selecting just video upload date

date <- details %>%
  filter(grepl("^2021", items)) %>%
  filter(!grepl("title", items)) %>%
  select(items) %>%
  unique()

#getting number of likes, comments, etc

dat_stats <- map_dfr(vids, get_stats)

stats <- dat_stats %>%
  mutate(views = as.numeric(viewCount)) %>%
  mutate(likes = as.numeric(likeCount)) %>%
  mutate(comments = as.numeric(commentCount))

class(date)

#adding date and title into stats df

stats <- cbind(stats, date, title)

```

##Scraping Comments

```{r}

dat_comments <- map_dfr(vids, get_all_comments) #110152 comments

head(dat_comments)

```

##Saving and Loading Scraped Data

```{r}

save(stats, vids, file = "../Data/video_stats.RData")
#load("../Data/video_stats.RData")

save(dat_comments, file = "../Data/video_comments.RData")
#load("../Data/video_comments.RData")

dat_comments <- dat_comments %>%
  mutate(title = if_else(videoId == "9SmQOZWNyWE", "'Permission to Dance' Performance",
                         if_else(videoId == "jzptPcPLCnA", "Speech at the UN",
                                 if_else(videoId == "wAXcMD5dOBA", "UN Interview",
                                         if_else(videoId == "NWwPyY7OHig", "Nightline Interview",
                                                 if_else(videoId == "wT6qgOBRrps", "Moon Speech",
                                                         if_else(videoId == "N11sD4isDRI", "Arirang Coverage",
                                                 "NA"))))))) %>%
  select(title, videoId, textDisplay, textOriginal, authorDisplayName, likeCount)

#write.csv(dat_comments, file = "../Data/all_comments.csv")

```


#Table of General Stats
```{r}

stat_tab <- stats %>%
  select(title, views, likes, comments)

rownames(stat_tab) <- c(1:6)
colnames(stat_tab) <- c("Title", "Views", "Likes", "Number of Comments")

stat_tab <- stat_tab %>%
  bind_rows(summarise_all(., funs(if(is.numeric(.)) sum(.) else "Total")))

stargazer(stat_tab, title = "Summary Statistics, BTS UN YouTube Videos", summary = F)

```


##Topic Models

#Performance Video
```{r}
#Filtering to performance video
perf <- dat_comments %>%
  filter(videoId == "9SmQOZWNyWE") %>%
  select(videoId, textDisplay)

#getting rid of emojis (messes with models)
perf$textDisplay <- gsub("[^\x01-\x7F]", "", perf$textDisplay)

#fixing weird punctuation with apostrophes and such
perf$textDisplay <- gsub("&#39;", "'", perf$textDisplay)

perf$textDisplay <- gsub("<br>", "", perf$textDisplay)

perf$textDisplay <- gsub("&quot;", "", perf$textDisplay)

#Tidy DF
tidy_df_perf <- perf %>% #ID for each document
  mutate(doc = row_number()) %>%  
  unnest_tokens(word, textDisplay) %>% #splitting out individual words
  anti_join(stop_words) %>%
  anti_join(get_stopwords(language = "es")) %>% #remove spanish stopwords
    filter(word != "href", word != "https", word != "https", word != "www.youtube.com", word != "9smqozwnywe", word != "amp") 

```

```{r}
#top words
tidy_df_perf %>%
    count(word, sort = TRUE)

#factor for doc ID
tidy_df_perf$doc <- as.factor(tidy_df_perf$doc)

#tf idf
df_tf_idf <- tidy_df_perf %>%
  count(doc, word, sort = TRUE) %>%
  bind_tf_idf(word, doc, n) %>%
  arrange(-tf_idf) %>%
  group_by(doc) %>%
  top_n(10) %>%
  ungroup 

#ggplot
ggs <- df_tf_idf %>%
  mutate(word = reorder_within(word, tf_idf, doc)) %>%
  ggplot(aes(word, tf_idf, fill = doc)) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ doc, scales = "free", ncol = 3) +
    scale_x_reordered() +
    coord_flip()


save(tidy_df_perf, ggs, df_tf_idf, file = "../Data/perf_dfs.RData")
load(file = "../Data/perf_dfs.RData")
```

##TOPIC MODEL##

#DFM
```{r}
#dfm
dfm <- tidy_df_perf %>%
    count(doc, word, sort = TRUE) %>%
    cast_dfm(doc, word, n)

dfm_sparse <- tidy_df_perf %>%
    count(doc, word, sort = TRUE) %>%
    cast_sparse(doc, word, n)

```

##Determine number of topics
```{r}
many_models <- data_frame(K = c(2, 3, 4, 5, 6, 7)) %>%
  mutate(topic_model = furrr::future_map(K, ~stm(dfm, K = .,
                                          verbose = FALSE)))

heldout <- make.heldout(dfm)

k_result <- many_models %>%
  mutate(exclusivity = map(topic_model, exclusivity),
         semantic_coherence = map(topic_model, semanticCoherence, dfm),
         eval_heldout = map(topic_model, eval.heldout, heldout$missing),
         residual = map(topic_model, checkResiduals, dfm),
         bound =  map_dbl(topic_model, function(x) max(x$convergence$bound)),
         lfact = map_dbl(topic_model, function(x) lfactorial(x$settings$dim$K)),
         lbound = bound + lfact,
         iterations = map_dbl(topic_model, function(x) length(x$convergence$bound)))

k_result


#pdf(file = "../Results/diagnostics_perf.pdf", width = 9, height = 9)

k_result %>%
  transmute(K,
            `Lower bound` = lbound,
            Residuals = map_dbl(residual, "dispersion"),
            `Semantic coherence` = map_dbl(semantic_coherence, mean),
            `Held-out likelihood` = map_dbl(eval_heldout, "expected.heldout")) %>%
  gather(Metric, Value, -K) %>%
  ggplot(aes(K, Value, color = Metric)) +
  geom_line(size = 1.5, alpha = 0.7, show.legend = FALSE) +
  facet_wrap(~Metric, scales = "free_y") +
  labs(x = "K (number of topics)",
       y = NULL,
       title = "BTS Performance Diagnostics by Number of Topics",
       subtitle = "These diagnostics indicate that a good number of topics would be around 3")

#dev.off()

save(many_models, k_result, file = "../Data/many_models_perf.RData")
#load(file = "../Data/many_models_perf.RData")


```


#Model!
```{r}

#basic model
topic_model <- stm(dfm, K =3, 
                   verbose = FALSE, init.type = "Spectral")

save(topic_model, file = "../Data/model_perf.RData")

#tidying
td_beta <- tidy(topic_model)


topic_ggs <- td_beta %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    mutate(topic = paste0("Topic ", topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = expression(beta),
         title = "Permission to Dance Performance Video Comments",
         subtitle = "Highest word probabilities for each topic")

#pdf(file = "../Results/topic_ggs_perf.pdf", width = 9, height = 9)

topic_ggs

#dev.off()
```



#Speech Video
```{r}
#Filtering to performance video
speech <- dat_comments %>%
  filter(videoId == "jzptPcPLCnA") %>%
  select(videoId, textDisplay)

#getting rid of emojis (messes with models)
speech$textDisplay <- gsub("[^\x01-\x7F]", "", speech$textDisplay)

#fixing weird punctuation with apostrophes and line breaks
speech$textDisplay <- gsub("&#39;", "'", speech$textDisplay)

speech$textDisplay <- gsub("<br>", "", speech$textDisplay)

speech$textDisplay <- gsub("&quot;", "", speech$textDisplay)

#Tidy DF
tidy_df_speech <- speech %>% #ID for each document
  mutate(doc = row_number()) %>%  
  unnest_tokens(word, textDisplay) %>% #splitting out individual words
  anti_join(stop_words) %>%
  anti_join(get_stopwords(language = "es")) %>% #remove spanish stopwords
    filter(word != "href", word != "https", word != "https", word != "www.youtube.com", word != "jzptPcPLCnA", word != "jzptpcplcna", word != "amp") 


```

#tf idf
```{r}
#top words
tidy_df_speech %>%
    count(word, sort = TRUE)

#factor for doc ID
tidy_df_speech$doc <- as.factor(tidy_df_speech$doc)

#tf idf
df_tf_idf <- tidy_df_speech %>%
  count(doc, word, sort = TRUE) %>%
  bind_tf_idf(word, doc, n) %>%
  arrange(-tf_idf) %>%
  group_by(doc) %>%
  top_n(10) %>%
  ungroup 

#ggplot
ggs <- df_tf_idf %>%
  mutate(word = reorder_within(word, tf_idf, doc)) %>%
  ggplot(aes(word, tf_idf, fill = doc)) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ doc, scales = "free", ncol = 3) +
    scale_x_reordered() +
    coord_flip()


save(tidy_df_speech, ggs, df_tf_idf, file = "../Data/speech_dfs.RData")
#load(file = "../Data/speech_dfs.RData")
```

##TOPIC MODEL##

#DFM
```{r}
#dfm
dfm <- tidy_df_speech %>%
    count(doc, word, sort = TRUE) %>%
    cast_dfm(doc, word, n)

dfm_sparse <- tidy_df_speech %>%
    count(doc, word, sort = TRUE) %>%
    cast_sparse(doc, word, n)

```


##Determne number of topics
```{r}
many_models <- data_frame(K = c(2, 3, 4, 5, 6, 7)) %>%
  mutate(topic_model = furrr::future_map(K, ~stm(dfm, K = .,
                                          verbose = FALSE)))

heldout <- make.heldout(dfm)

k_result <- many_models %>%
  mutate(exclusivity = map(topic_model, exclusivity),
         semantic_coherence = map(topic_model, semanticCoherence, dfm),
         eval_heldout = map(topic_model, eval.heldout, heldout$missing),
         residual = map(topic_model, checkResiduals, dfm),
         bound =  map_dbl(topic_model, function(x) max(x$convergence$bound)),
         lfact = map_dbl(topic_model, function(x) lfactorial(x$settings$dim$K)),
         lbound = bound + lfact,
         iterations = map_dbl(topic_model, function(x) length(x$convergence$bound)))

k_result


#pdf(file = "../Results/diagnostics_speech.pdf", width = 9, height = 9)

k_result %>%
  transmute(K,
            `Lower bound` = lbound,
            Residuals = map_dbl(residual, "dispersion"),
            `Semantic coherence` = map_dbl(semantic_coherence, mean),
            `Held-out likelihood` = map_dbl(eval_heldout, "expected.heldout")) %>%
  gather(Metric, Value, -K) %>%
  ggplot(aes(K, Value, color = Metric)) +
  geom_line(size = 1.5, alpha = 0.7, show.legend = FALSE) +
  facet_wrap(~Metric, scales = "free_y") +
  labs(x = "K (number of topics)",
       y = NULL,
       title = "BTS Speech Diagnostics by Number of Topics",
       subtitle = "These diagnostics indicate that a good number of topics would be around 4")

#dev.off()

save(many_models, k_result, file = "../Data/many_models_speech.RData")
#load(file = "../Data/many_models_speech.RData")

```

#Model!
```{r}

#basic model
topic_model <- stm(dfm, K = 4, 
                   verbose = FALSE, init.type = "Spectral")

save(topic_model, file = "../Data/model_speech.RData")

#tidying
td_beta <- tidy(topic_model)


topic_ggs <- td_beta %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    mutate(topic = paste0("Topic ", topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = expression(beta),
         title = "BTS UN Speech Video Comments",
         subtitle = "Highest word probabilities for each topic")


#pdf(file = "../Results/topic_ggs_speech.pdf", width = 9, height = 9)

topic_ggs

#dev.off()
```




#UN Interview
```{r}
#Filtering to performance video
un <- dat_comments %>%
  filter(videoId == "wAXcMD5dOBA") %>%
  select(videoId, textDisplay)

#getting rid of emojis (messes with models)
un$textDisplay <- gsub("[^\x01-\x7F]", "", un$textDisplay)

#fixing weird punctuation with apostrophes and line breaks
un$textDisplay <- gsub("&#39;", "'", un$textDisplay)

un$textDisplay <- gsub("<br>", "", un$textDisplay)

un$textDisplay <- gsub("&quot;", "", un$textDisplay)

#Tidy DF
tidy_df_un <- un %>% #ID for each document
  mutate(doc = row_number()) %>%  
  unnest_tokens(word, textDisplay) %>% #splitting out individual words
  anti_join(stop_words) %>%
  anti_join(get_stopwords(language = "es")) %>% #remove spanish stopwords
  filter(word != "href", word != "https", word != "https", word != "www.youtube.com", word != "wAXcMD5dOBA", word != "waxcmd5doba", word != "amp") 

```


#tf idf
```{r}
#top words
tidy_df_un %>%
    count(word, sort = TRUE)

#factor for doc ID
tidy_df_un$doc <- as.factor(tidy_df_un$doc)

#tf idf
df_tf_idf <- tidy_df_un %>%
  count(doc, word, sort = TRUE) %>%
  bind_tf_idf(word, doc, n) %>%
  arrange(-tf_idf) %>%
  group_by(doc) %>%
  top_n(10) %>%
  ungroup 

#ggplot
ggs <- df_tf_idf %>%
  mutate(word = reorder_within(word, tf_idf, doc)) %>%
  ggplot(aes(word, tf_idf, fill = doc)) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ doc, scales = "free", ncol = 3) +
    scale_x_reordered() +
    coord_flip()


save(tidy_df_un, ggs, df_tf_idf, file = "../Data/un_dfs.RData")
load(file = "../Data/un_dfs.RData")

```

##TOPIC MODEL##

#DFM
```{r}
#dfm
dfm <- tidy_df_un %>%
    count(doc, word, sort = TRUE) %>%
    cast_dfm(doc, word, n)

dfm_sparse <- tidy_df_un %>%
    count(doc, word, sort = TRUE) %>%
    cast_sparse(doc, word, n)

```

##Determne number of topics
```{r}
many_models <- data_frame(K = c(2, 3, 4, 5, 6, 7)) %>%
  mutate(topic_model = furrr::future_map(K, ~stm(dfm, K = .,
                                          verbose = FALSE)))

heldout <- make.heldout(dfm)

k_result <- many_models %>%
  mutate(exclusivity = map(topic_model, exclusivity),
         semantic_coherence = map(topic_model, semanticCoherence, dfm),
         eval_heldout = map(topic_model, eval.heldout, heldout$missing),
         residual = map(topic_model, checkResiduals, dfm),
         bound =  map_dbl(topic_model, function(x) max(x$convergence$bound)),
         lfact = map_dbl(topic_model, function(x) lfactorial(x$settings$dim$K)),
         lbound = bound + lfact,
         iterations = map_dbl(topic_model, function(x) length(x$convergence$bound)))

k_result

#pdf(file = "../Results/diagnostics_un.pdf", width = 9, height = 9)

k_result %>%
  transmute(K,
            `Lower bound` = lbound,
            Residuals = map_dbl(residual, "dispersion"),
            `Semantic coherence` = map_dbl(semantic_coherence, mean),
            `Held-out likelihood` = map_dbl(eval_heldout, "expected.heldout")) %>%
  gather(Metric, Value, -K) %>%
  ggplot(aes(K, Value, color = Metric)) +
  geom_line(size = 1.5, alpha = 0.7, show.legend = FALSE) +
  facet_wrap(~Metric, scales = "free_y") +
  labs(x = "K (number of topics)",
       y = NULL,
       title = "UN Interview Diagnostics by Number of Topics",
       subtitle = "These diagnostics indicate that a good number of topics would be around 4")

#dev.off()

save(many_models, k_result, file = "../Data/many_models_un.RData")
#load(file = "../Data/many_models_un.RData")

```


#Model

```{r}

#basic model
topic_model <- stm(dfm, K = 4, 
                   verbose = FALSE, init.type = "Spectral")

save(topic_model, file = "../Data/model_un.RData")
load(file = "../Data/model_un.RData")

#tidying
td_beta <- tidy(topic_model)


topic_ggs <- td_beta %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    mutate(topic = paste0("Topic ", topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = expression(beta),
         title = "BTS and Moon UN Interview Video Comments",
         subtitle = "Highest word probabilities for each topic")


#pdf(file = "../Results/topic_ggs_un.pdf", width = 9, height = 9)

topic_ggs

#dev.off()
```






#ABC Interview
```{r}
#Filtering to performance video
abc <- dat_comments %>%
  filter(videoId == "NWwPyY7OHig") %>%
  select(videoId, textDisplay)

#getting rid of emojis (messes with models)
abc$textDisplay <- gsub("[^\x01-\x7F]", "", abc$textDisplay)

#fixing weird punctuation with apostrophes and line breaks
abc$textDisplay <- gsub("&#39;", "'", abc$textDisplay)

abc$textDisplay <- gsub("<br>", "", abc$textDisplay)

abc$textDisplay <- gsub("&quot;", "", abc$textDisplay)

#Tidy DF
tidy_df_abc <- abc %>% #ID for each document
  mutate(doc = row_number()) %>%  
  unnest_tokens(word, textDisplay) %>% #splitting out individual words
  anti_join(stop_words) %>%
  anti_join(get_stopwords(language = "es")) %>% #remove spanish stopwords
  filter(word != "href", word != "https", word != "https", word != "www.youtube.com", word != "NWwPyY7OHig", word != "nwwpyy7ohig", word != "amp", word != "youtu.be", word != "http") 

```

#tf idf
```{r}
#top words
tidy_df_abc %>%
    count(word, sort = TRUE)

#factor for doc ID
tidy_df_abc$doc <- as.factor(tidy_df_abc$doc)

#tf idf
df_tf_idf <- tidy_df_abc %>%
  count(doc, word, sort = TRUE) %>%
  bind_tf_idf(word, doc, n) %>%
  arrange(-tf_idf) %>%
  group_by(doc) %>%
  top_n(10) %>%
  ungroup 

#ggplot
ggs <- df_tf_idf %>%
  mutate(word = reorder_within(word, tf_idf, doc)) %>%
  ggplot(aes(word, tf_idf, fill = doc)) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ doc, scales = "free", ncol = 3) +
    scale_x_reordered() +
    coord_flip()


save(tidy_df_abc, ggs, df_tf_idf, file = "../Data/abc_dfs.RData")
```



##TOPIC MODEL##

#DFM
```{r}
#dfm
dfm <- tidy_df_abc %>%
    count(doc, word, sort = TRUE) %>%
    cast_dfm(doc, word, n)

dfm_sparse <- tidy_df_abc %>%
    count(doc, word, sort = TRUE) %>%
    cast_sparse(doc, word, n)

```

##Determne number of topics
```{r}
many_models <- data_frame(K = c(2, 3, 4, 5, 6, 7, 8)) %>%
  mutate(topic_model = furrr::future_map(K, ~stm(dfm, K = .,
                                          verbose = FALSE)))

heldout <- make.heldout(dfm)

k_result <- many_models %>%
  mutate(exclusivity = map(topic_model, exclusivity),
         semantic_coherence = map(topic_model, semanticCoherence, dfm),
         eval_heldout = map(topic_model, eval.heldout, heldout$missing),
         residual = map(topic_model, checkResiduals, dfm),
         bound =  map_dbl(topic_model, function(x) max(x$convergence$bound)),
         lfact = map_dbl(topic_model, function(x) lfactorial(x$settings$dim$K)),
         lbound = bound + lfact,
         iterations = map_dbl(topic_model, function(x) length(x$convergence$bound)))

k_result

#pdf(file = "../Results/diagnostics_abc.pdf", width = 9, height = 9)

k_result %>%
  transmute(K,
            `Lower bound` = lbound,
            Residuals = map_dbl(residual, "dispersion"),
            `Semantic coherence` = map_dbl(semantic_coherence, mean),
            `Held-out likelihood` = map_dbl(eval_heldout, "expected.heldout")) %>%
  gather(Metric, Value, -K) %>%
  ggplot(aes(K, Value, color = Metric)) +
  geom_line(size = 1.5, alpha = 0.7, show.legend = FALSE) +
  facet_wrap(~Metric, scales = "free_y") +
  labs(x = "K (number of topics)",
       y = NULL,
       title = "ABC Interview Diagnostics by Number of Topics",
       subtitle = "These diagnostics indicate that a good number of topics would be around 4")

#dev.off()

save(many_models, k_result, file = "../Data/many_models_abc.RData")
load(file = "../Data/many_models_abc.RData")

```


#Model!
```{r}

#basic model
topic_model <- stm(dfm, K = 4, 
                   verbose = FALSE, init.type = "Spectral")

save(topic_model, file = "../Data/model_abc.RData")

#tidying
td_beta <- tidy(topic_model)


topic_ggs <- td_beta %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    mutate(topic = paste0("Topic ", topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = expression(beta),
         title = "BTS and Moon ABC Interview Video Comments",
         subtitle = "Highest word probabilities for each topic")

#pdf(file = "../Results/topic_ggs_abc.pdf", width = 9, height = 9)

topic_ggs

#dev.off()
```






#Moon Speech
```{r}
#Filtering to performance video
moon <- dat_comments %>%
  filter(videoId == "wT6qgOBRrps") %>%
  select(videoId, textDisplay)

#getting rid of emojis (messes with models)
moon$textDisplay <- gsub("[^\x01-\x7F]", "", moon$textDisplay)

#fixing weird punctuation with apostrophes and line breaks
moon$textDisplay <- gsub("&#39;", "'", moon$textDisplay)

moon$textDisplay <- gsub("<br>", "", moon$textDisplay)

moon$textDisplay <- gsub("&quot;", "", moon$textDisplay)

#Tidy DF
tidy_df_moon <- moon %>% #ID for each document
  mutate(doc = row_number()) %>%  
  unnest_tokens(word, textDisplay) %>% #splitting out individual words
  anti_join(stop_words) %>%
  anti_join(get_stopwords(language = "es")) %>% #remove spanish stopwords
  filter(word != "href", word != "https", word != "https", word != "www.youtube.com", word != "wT6qgOBRrps", word != "wt6qgobrrps", word != "amp") 

```


#tf idf
```{r}
#top words
tidy_df_moon %>%
    count(word, sort = TRUE)

#factor for doc ID
tidy_df_moon$doc <- as.factor(tidy_df_moon$doc)

#tf idf
df_tf_idf <- tidy_df_moon %>%
  count(doc, word, sort = TRUE) %>%
  bind_tf_idf(word, doc, n) %>%
  arrange(-tf_idf) %>%
  group_by(doc) %>%
  top_n(10) %>%
  ungroup 

#ggplot
ggs <- df_tf_idf %>%
  mutate(word = reorder_within(word, tf_idf, doc)) %>%
  ggplot(aes(word, tf_idf, fill = doc)) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ doc, scales = "free", ncol = 3) +
    scale_x_reordered() +
    coord_flip()


save(tidy_df_moon, ggs, df_tf_idf, file = "../Data/moon_dfs.RData")
```

##TOPIC MODEL##

#DFM
```{r}
#dfm
dfm <- tidy_df_moon %>%
    count(doc, word, sort = TRUE) %>%
    cast_dfm(doc, word, n)

dfm_sparse <- tidy_df_moon %>%
    count(doc, word, sort = TRUE) %>%
    cast_sparse(doc, word, n)

```

##Determne number of topics
```{r}
many_models <- data_frame(K = c(2, 3, 4, 5, 6, 7)) %>%
  mutate(topic_model = furrr::future_map(K, ~stm(dfm, K = .,
                                          verbose = FALSE)))

heldout <- make.heldout(dfm)

k_result <- many_models %>%
  mutate(exclusivity = map(topic_model, exclusivity),
         semantic_coherence = map(topic_model, semanticCoherence, dfm),
         eval_heldout = map(topic_model, eval.heldout, heldout$missing),
         residual = map(topic_model, checkResiduals, dfm),
         bound =  map_dbl(topic_model, function(x) max(x$convergence$bound)),
         lfact = map_dbl(topic_model, function(x) lfactorial(x$settings$dim$K)),
         lbound = bound + lfact,
         iterations = map_dbl(topic_model, function(x) length(x$convergence$bound)))

k_result

#pdf(file = "../Results/diagnostics_moon.pdf", width = 9, height = 9)

k_result %>%
  transmute(K,
            `Lower bound` = lbound,
            Residuals = map_dbl(residual, "dispersion"),
            `Semantic coherence` = map_dbl(semantic_coherence, mean),
            `Held-out likelihood` = map_dbl(eval_heldout, "expected.heldout")) %>%
  gather(Metric, Value, -K) %>%
  ggplot(aes(K, Value, color = Metric)) +
  geom_line(size = 1.5, alpha = 0.7, show.legend = FALSE) +
  facet_wrap(~Metric, scales = "free_y") +
  labs(x = "K (number of topics)",
       y = NULL,
       title = "Moon Speech Diagnostics by Number of Topics",
       subtitle = "These diagnostics indicate that a good number of topics would be around 4")

#dev.off()

save(many_models, k_result, file = "../Data/many_models_moon.RData")
#load(file = "../Data/many_models_moon.RData")

```



#Model

```{r}

#basic model
topic_model <- stm(dfm, K = 4, 
                   verbose = FALSE, init.type = "Spectral")

save(topic_model, file = "../Data/model_moon.RData")

#tidying
td_beta <- tidy(topic_model)


topic_ggs <- td_beta %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    mutate(topic = paste0("Topic ", topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = expression(beta),
         title = "Moon UN Speech Video Comments",
         subtitle = "Highest word probabilities for each topic")

#pdf(file = "../Results/topic_ggs_moon.pdf", width = 9, height = 9)

topic_ggs

#dev.off()
```







#Arirang
```{r}
#Filtering to performance video
arirang <- dat_comments %>%
  filter(videoId == "N11sD4isDRI") %>%
  select(videoId, textDisplay)

#getting rid of emojis (messes with models)
arirang$textDisplay <- gsub("[^\x01-\x7F]", "", arirang$textDisplay)

#fixing weird punctuation with apostrophes and line breaks
arirang$textDisplay <- gsub("&#39;", "'", arirang$textDisplay)

arirang$textDisplay <- gsub("<br>", "", arirang$textDisplay)

arirang$textDisplay <- gsub("&quot;", "", arirang$textDisplay)

#Tidy DF
tidy_df_arirang <- arirang %>% #ID for each document
  mutate(doc = row_number()) %>%  
  unnest_tokens(word, textDisplay) %>% #splitting out individual words
  anti_join(stop_words) %>%
  anti_join(get_stopwords(language = "es")) %>% #remove spanish stopwords
  filter(word != "href", word != "https", word != "https", word != "www.youtube.com", word != "N11sD4isDRI", word != "n11sd4isdri", word != "amp", word != "search_query", word != "http") 


```


#tf idf
```{r}
#top words
tidy_df_arirang %>%
    count(word, sort = TRUE)

#factor for doc ID
tidy_df_arirang$doc <- as.factor(tidy_df_arirang$doc)

#tf idf
df_tf_idf <- tidy_df_arirang %>%
  count(doc, word, sort = TRUE) %>%
  bind_tf_idf(word, doc, n) %>%
  arrange(-tf_idf) %>%
  group_by(doc) %>%
  top_n(10) %>%
  ungroup 

#ggplot
ggs <- df_tf_idf %>%
  mutate(word = reorder_within(word, tf_idf, doc)) %>%
  ggplot(aes(word, tf_idf, fill = doc)) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ doc, scales = "free", ncol = 3) +
    scale_x_reordered() +
    coord_flip()


save(tidy_df_arirang, ggs, df_tf_idf, file = "../Data/arirang_dfs.RData")
load(file = "../Data/arirang_dfs.RData")

```



##TOPIC MODEL##

#DFM
```{r}
#dfm
dfm <- tidy_df_arirang %>%
    count(doc, word, sort = TRUE) %>%
    cast_dfm(doc, word, n)

dfm_sparse <- tidy_df_arirang %>%
    count(doc, word, sort = TRUE) %>%
    cast_sparse(doc, word, n)

```

##Determne number of topics
```{r}
many_models <- data_frame(K = c(2, 3, 4, 5, 6, 7)) %>%
  mutate(topic_model = furrr::future_map(K, ~stm(dfm, K = .,
                                          verbose = FALSE)))

heldout <- make.heldout(dfm)

k_result <- many_models %>%
  mutate(exclusivity = map(topic_model, exclusivity),
         semantic_coherence = map(topic_model, semanticCoherence, dfm),
         eval_heldout = map(topic_model, eval.heldout, heldout$missing),
         residual = map(topic_model, checkResiduals, dfm),
         bound =  map_dbl(topic_model, function(x) max(x$convergence$bound)),
         lfact = map_dbl(topic_model, function(x) lfactorial(x$settings$dim$K)),
         lbound = bound + lfact,
         iterations = map_dbl(topic_model, function(x) length(x$convergence$bound)))

k_result

#pdf(file = "../Results/diagnostics_arirang.pdf", width = 9, height = 9)

k_result %>%
  transmute(K,
            `Lower bound` = lbound,
            Residuals = map_dbl(residual, "dispersion"),
            `Semantic coherence` = map_dbl(semantic_coherence, mean),
            `Held-out likelihood` = map_dbl(eval_heldout, "expected.heldout")) %>%
  gather(Metric, Value, -K) %>%
  ggplot(aes(K, Value, color = Metric)) +
  geom_line(size = 1.5, alpha = 0.7, show.legend = FALSE) +
  facet_wrap(~Metric, scales = "free_y") +
  labs(x = "K (number of topics)",
       y = NULL,
       title = "Arirang Coverage Diagnostics by Number of Topics",
       subtitle = "These diagnostics indicate that a good number of topics would be around 3")

#dev.off()

save(many_models, k_result, file = "../Data/many_models_arirang.RData")
#load(file = "../Data/many_models_arirang.RData")

```


#Model!
```{r}

#basic model
topic_model <- stm(dfm, K = 3, 
                   verbose = FALSE, init.type = "Spectral")

save(topic_model, file = "../Data/model_arirang.RData")

#tidying
td_beta <- tidy(topic_model)


topic_ggs <- td_beta %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    mutate(topic = paste0("Topic ", topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = expression(beta),
         title = "Arirang News Coverage Video Comments",
         subtitle = "Highest word probabilities for each topic")

#pdf(file = "../Results/topic_ggs_arirang.pdf", width = 9, height = 9)

topic_ggs

#dev.off()
```




#All videos together

```{r}
comments <- dat_comments$textDisplay

#getting rid of emojis (messes with models)
comments <- gsub("[^\x01-\x7F]", "", comments)

#fixing weird punctuation with apostrophes and line breaks
comments <- gsub("&#39;", "'", comments)

comments <- gsub("<br>", "", comments)

comments <- gsub("&quot;", "", comments)

#remove Spanish stopwords (they showed up in eventual clusters)
sp <- stopwords(kind = "sp")

comments_cleaned <- remove_stopwords(comments, words = tm::stopwords("spanish"), lines = T)


#Corpus
doc_comments <- Corpus(VectorSource(comments_cleaned))

#DTM
dtm_comments <- DocumentTermMatrix(doc_comments,
           control = list(stopwords = TRUE,
                          tolower = TRUE,
                          removeNumbers = TRUE,
                          removePunctuation = TRUE,
                          stemming=TRUE))


dtm_comments #very high sparsity!

comments_subset <- removeSparseTerms(dtm_comments, 0.995)

comments_subset


```

#K-means
```{r}

matrix_comments <- as.matrix(comments_subset)

#Determine number of clusters
k <- 7
varper <- NULL
for (i in 1:k) {
    kfit <- kmeans(matrix_comments, i)
    varper <- c(varper, kfit$betweenss/kfit$totss)
}
varper

plot(1:k, varper, xlab = "# of clusters", ylab = "explained variance")

#K-means
kfit_comments <- kmeans(matrix_comments, 4)

kfit_comments

#Visualizing

clusplot(matrix_comments, kfit_comments$cluster, color=TRUE, shade=TRUE, 
         labels=3, lines=0)

clustering<-kfit_comments$cluster
p_words <- colSums(matrix_comments) / sum(matrix_comments)

cluster_words <- lapply(unique(clustering), function(x){
  rows <- matrix_comments[clustering == x , ]
  
  # for memory's sake, drop all words that don't appear in the cluster
  rows <- rows[ , colSums(as.matrix(rows)) > 0 ]
  
  colSums(as.matrix(rows)) / sum(as.matrix(rows)) - p_words[ colnames(as.matrix(rows)) ]
})

cluster_summary <- data.frame(cluster = unique(clustering),
                              size = as.numeric(table(clustering)),
                              top_words = sapply(cluster_words, function(d){
                                paste(
                                  names(d)[ order(d, decreasing = TRUE) ][ 1:5 ], 
                                  collapse = ", ")
                              }),
                              stringsAsFactors = FALSE)
cluster_summary

```


##Frequent Terms

#Speech Video

```{r}

dtm_speech <- DocumentTermMatrix(doc_speech,
           control = list(stopwords = TRUE,
                          tolower = TRUE,
                          removeNumbers = TRUE,
                          removePunctuation = TRUE,
                          stemming=TRUE))

weighted_dtm_speech <- DocumentTermMatrix(doc_speech,
           control = list(weighting =function(x) weightTfIdf(x, normalize = TRUE),
                          stopwords = TRUE,
                          tolower = TRUE,
                          removeNumbers = TRUE,
                          removePunctuation = TRUE,
                          stemming=TRUE))

dim(dtm_speech) #9368 and 15915

```

#UN Interview Video
```{r}

dtm_un <- DocumentTermMatrix(doc_un,
           control = list(stopwords = TRUE,
                          tolower = TRUE,
                          removeNumbers = TRUE,
                          removePunctuation = TRUE,
                          stemming=TRUE))

weighted_dtm_un <- DocumentTermMatrix(doc_un,
           control = list(weighting =function(x) weightTfIdf(x, normalize = TRUE),
                          stopwords = TRUE,
                          tolower = TRUE,
                          removeNumbers = TRUE,
                          removePunctuation = TRUE,
                          stemming=TRUE))

dim(dtm_un) #121593 and 22233


```

#ABC Interview Video
```{r}

dtm_abc <- DocumentTermMatrix(doc_abc,
           control = list(stopwords = TRUE,
                          tolower = TRUE,
                          removeNumbers = TRUE,
                          removePunctuation = TRUE,
                          stemming=TRUE))

weighted_dtm_abc <- DocumentTermMatrix(doc_abc,
           control = list(weighting =function(x) weightTfIdf(x, normalize = TRUE),
                          stopwords = TRUE,
                          tolower = TRUE,
                          removeNumbers = TRUE,
                          removePunctuation = TRUE,
                          stemming=TRUE))

dim(dtm_abc) #2616 and 6901


```



```{r}
#TF-IDF
dtm_speech <- weightTfIdf(dtm_speech, normalize = TRUE)
matrix_speech = as.matrix(dtm_speech)

dtm_un <- weightTfIdf(dtm_un, normalize = TRUE)
matrix_un <- as.matrix(dtm_un)

dtm_abc <- weightTfIdf(dtm_abc, normalize = TRUE)
matrix_abc = as.matrix(dtm_abc)
```



##Exploring frequent terms

#Performance
```{r}

freq_perf <- colSums(as.matrix(weighted_dtm_perf))

# order
dtm_ordered_perf <- weighted_dtm_perf[,order(freq_perf, decreasing = T)]

inspect(dtm_ordered_perf[1:5,1:5])
top_5_perf <- dtm_ordered_perf[["dimnames"]][["Terms"]][1:5]

findFreqTerms(dtm_ordered_perf, lowfreq=500)

findAssocs(weighted_dtm_perf, "bts", 0.01)

```


#Speech
```{r}

freq_speech <- colSums(as.matrix(weighted_dtm_speech))

# order
dtm_ordered_speech <- weighted_dtm_speech[,order(freq_speech, decreasing = T)]

inspect(dtm_ordered_speech[1:5,1:5])
top_10_speech <- dtm_ordered_speech[["dimnames"]][["Terms"]][1:10]

findFreqTerms(dtm_ordered_speech, lowfreq=500)

#####Start here for Table of Related Terms
pres_1 <- findAssocs(weighted_dtm_speech, "presid", 0.09)
pres_2 <- findAssocs(weighted_dtm_un, "presid", 0.05)
#pres_3 <- 
  
  findAssocs(weighted_dtm_abc, "presid", 0.09)

pres_2 <- pres_2[[1:12]]

pres <- data_frame(pres_1$presid, pres_2$presid, pres_3$presid)
```

#UN
```{r}

freq_un <- colSums(as.matrix(weighted_dtm_un))

# order
dtm_ordered_un <- weighted_dtm_un[,order(freq_un, decreasing = T)]

inspect(dtm_ordered_un[1:5,1:5])
top_10_un <- dtm_ordered_un[["dimnames"]][["Terms"]][1:10]

findFreqTerms(dtm_ordered_un, lowfreq=500)

findAssocs(weighted_dtm_un, "presid", 0.01)

```

#ABC
```{r}

freq_abc <- colSums(as.matrix(weighted_dtm_abc))

# order
dtm_ordered_abc <- weighted_dtm_abc[,order(freq_abc, decreasing = T)]

inspect(dtm_ordered_abc[1:5,1:5])
top_10_abc <- dtm_ordered_abc[["dimnames"]][["Terms"]][1:10]

findFreqTerms(dtm_ordered_abc, lowfreq=500)

findAssocs(weighted_dtm_abc, "presid", 0.01)

```

#Top Freq Terms
```{r}
top_10 <- data.frame(top_10_perf, top_10_speech, top_10_un, top_10_abc)

save(top_10, file = "../Data/top_10_terms.RData")
```